Comparing Machine Learning and Traditional Regression Methods in Site-Specific Economically Optimal Nitrogen Rate Prediction

### 2022-02-09 Writing/manuscript.rmd
manuscript writing

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(gridExtra)
```

@@

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
# fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
#   lapply(., function(x) source(x))

# /*----------------------------------*/
#' ##  data preparation
# /*----------------------------------*/
#' load results data
est_data <-
  readRDS(here("Results", "est_result_ls_400.rds")) %>%
  rbindlist() %>%
  dplyr::select(model, perform, field_col) %>%
  unnest(perform) %>%
  data.table()
#' rename columns
gdata <- est_data %>%
  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv)] %>%
  #---field size---
  .[, field_size := paste0(round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
  .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>%
  #---model name---
  .[model == "brf", model := "BRF"] %>%
  .[model == "rf", model := "RF"] %>%
  .[model == "rf_perfect", model := "RF best"] %>%
  .[model == "lm", model := "LM"] %>%
  .[model == "ser_50", model := "SER"] %>%
  .[, model := factor(model, levels = c("RF", "RF best", "BRF", "LM", "SER"))]
#' mean and sd
mean_data <- gdata %>%
  .[, .(
    profit = mean(profit) %>% round(2),
    profit_sd = sd(profit) %>% round(2),
    rmse = mean(rmse_cv) %>% round(2),
    rmse_sd = sd(rmse_cv) %>% round(2)
  ),
  by = c("field_size", "model")
  ] %>%
  .[order(field_size, model), ]

# /*----------------------------------*/
#' ##  create figures and tables
# /*----------------------------------*/
source(here("Codes", "3_make_figures_tables.R"))
```

@@

# Results

## Yield predictions
Machine learning methods perform better than traditional regression methods in yield prediction.  The RMSE results for the out-of-sample yield prediction over the 1,000 simulations are displayed in Figure \@ref(fig:rmse-boxplot-pool).

- For the full field (37.3 ha) scenario, the average RMSE over 1,000 simulations is `r mean_data[field_size=="37.3 ha"&model=="RF", rmse] %>% round(2)` kg ha$^{-1}$ for the RF model, and `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse] %>% round(2)` kg ha$^{-1}$ for the BRF model, which are significantly smaller than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse] %>% round(2)` kg ha$^{-1}$) and SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse] %>% round(2)` kg ha$^{-1}$) models.  If we give RF model the best data, its RMSE will be as small as `r mean_data[field_size=="37.3 ha"&model=="RF best", rmse] %>% round(2)` kg ha$^{-1}$.
- The trend of RMSE performance is robust to field sizes.  For smaller field sizes, the overall levels of RMSE are slightly larger (of course), but machine learning models' RMSE (RF and BRF) are consistently smaller than the RMSE of traditional regression models (LM and SER).

@@

@@

Profit performance results for different models are displayed in Figure \@ref(fig:pi-boxplot-pool).

@@

# Discussions

+ Yield prediction vs EONR prediction
+ Statistical efficiency is money (SER vs LM)

@@

```{r rmse-boxplot-pool, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
rmse_boxplot_pool | pi_boxplot_pool
```

```{r pi-boxplot-pool, fig.cap="The profit performances of different models.", echo=FALSE}
pi_boxplot_pool
```

@@

```{r extreme-percent, echo=FALSE}
knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics")
```

>>>>

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(gridExtra)
library(kableExtra)
library(here)
```

@@

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================

#* source all the functions in the Functions folder
# fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
#   lapply(., function(x) source(x))

# /*----------------------------------*/
#' ##  data preparation
# /*----------------------------------*/
#' load results data
est_data <-
  readRDS(here("Shared", "Results", "est_result_ls.rds")) %>%
  rbindlist() %>%
  dplyr::select(model, perform, field_col) %>%
  unnest(perform) %>%
  data.table()
#' rename columns
gdata <- est_data %>%
  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv, rmse_eonr)] %>%
  #---field size---
  .[, field_size := paste0(round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
  .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>%
  #---model name---
  .[model == "brf", model := "BRF"] %>%
  .[model == "rf", model := "RF"] %>%
  .[model == "rf_perfect", model := "RF best"] %>%
  .[model == "lm", model := "LM"] %>%
  .[model == "ser_50", model := "SER"] %>%
  .[, model := factor(model, levels = c("RF", "RF best", "BRF", "LM", "SER"))]
#' mean and sd
mean_data <- gdata %>%
  .[, .(
    profit = mean(profit) %>% round(2),
    profit_sd = sd(profit) %>% round(2),
    rmse_yield = mean(rmse_cv) %>% round(2),
    rmse_yield_sd = sd(rmse_cv) %>% round(2),
    rmse_eonr = mean(rmse_eonr) %>% round(2),
    rmse_eonr_sd = sd(rmse_eonr) %>% round(2)
  ),
  by = c("field_size", "model")
  ] %>%
  .[order(field_size, model), ]

# /*----------------------------------*/
#' ##  create figures and tables
# /*----------------------------------*/
source(here("GitControlled", "Codes", "3_make_figures_tables.R"))
```

@@

# Results and Discussions

## Yield predictions
Machine learning methods perform better than traditional regression methods in yield prediction.  The RMSE results for the out-of-sample yield prediction over the 1,000 simulations are displayed in Figure \@ref(fig:rmse-yield-boxplot).

- For the full field (37.3 ha) scenario, the average RMSE over 1,000 simulations is `r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$ for the RF model, and `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$ for the BRF model, which are significantly smaller than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_yield] %>% round(2)` kg ha$^{-1}$) and SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) models.  If we give RF model the best data, its RMSE will be as small as `r mean_data[field_size=="37.3 ha"&model=="RF best", rmse_yield] %>% round(2)` kg ha$^{-1}$.
- The trend of RMSE performance is robust to field sizes.  For smaller field sizes, the overall levels of RMSE are slightly larger (of course), but machine learning models' RMSE (RF and BRF) are consistently smaller than the RMSE of traditional regression models (LM and SER).

@@

EONR prediction performances for different models are displayed in Figure \@ref(fig:rmse-eonr-boxplot).

@@

Profit performance results for different models are displayed in Figure \@ref(fig:pi-boxplot).

@@

@@

```{r rmse-yield-boxplot, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
rmse_yield_boxplot
```

```{r rmse-eonr-boxplot, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
rmse_eonr_boxplot
```

```{r pi-boxplot, fig.cap="The profit performances of different models.", echo=FALSE, fig.width=7}
pi_boxplot
```

@@

```{r extreme-percent, echo=FALSE}
# knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics") %>% 
#  kable_styling(font_size = 3)
```
